Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Add missing citations in the introduction #54

@@

>>>>

\bibitem{} Cerra, Valerie, and Sweta Chaman Saxena. 2008. ``Growth Dynamics: The Myth of Economic Recovery.'' \textit{American Economic Review}, 98(1): 439--457.
\bibitem{} Davis, Donald, and Davis Weinstein. 2002. ``Bones, Bombs, and Break Points: The Geography of Economic Activity.'' \textit{American Economic Review}, 92(5): 1296--1289.

@@

\bibitem{} Miguel, Edward, and Gerard Roland. 2011. ``The Long-Run Impact of Bombing Vietnam.'' \textit{Journal of Development Economics}, 96(1): 1--15.
